\documentclass[10pt]{article}

%% Define some new colors
\usepackage{xcolor}
\definecolor{mBlue}{RGB}{51, 77, 167}
\newcommand{\blue}[1]{{\color{mBlue}#1}}

%% Page and text formatting
\usepackage[left=1.0in, right=1.0in, top=1.0in, bottom=1.0in]{geometry} % margins
\usepackage{setspace}
\singlespacing % No more than 6 lines of text per inch
\usepackage{amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{helvet}
% \usepackage{lmodern}

%% Make the sections start with (a), (b), etc.
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

%% Set up footer
\usepackage{fancyhdr}
\fancypagestyle{CVfooter}
{
 \lhead{}
 \chead{}
 \rhead{}
 \lfoot{\sffamily\helvet\small{Patrick V.\ Phaneuf}}
 \cfoot{\sffamily\helvet\small{\today}}
 \rfoot{\sffamily\helvet\small{\thepage/2}}
 \renewcommand{\headrulewidth}{0.0pt}
 \renewcommand{\footrulewidth}{0.5pt}
}

%% Set up hyperlinks
\usepackage[linktoc=page]{hyperref}
\hypersetup{
  colorlinks = true,
  urlcolor = mBlue,
  citecolor = mBlue,
  linkcolor = mBlue,
}

%% Set up citations and bibliography
\usepackage{bibunits}
\usepackage[sort&compress,super]{natbib}
\defaultbibliographystyle{apsrev4-2}
\setcitestyle{comma}
\setlength{\bibsep}{0pt}
\renewcommand{\bibnumfmt}[1]{\ \ \ #1.}
\renewcommand\refname{\vspace{-7mm}}

%% This allows us to start a bibliography with arbitrary number
\usepackage{etoolbox}
\makeatletter
\newcommand*{\newbibstartnumber}[1]{%
  \apptocmd{\thebibliography}{%
    \global\c@NAT@ctr #1\relax
    \addtocounter{NAT@ctr}{-1}%
  }{}{}%
}
\makeatother

%% Reduce whitespace around lists (globally)
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt}
\setlist[enumerate]{nosep}
\setlist[description]{nosep}

%% Formatting for sections
\usepackage[compact]{titlesec}
\titleformat*{\section}{\normalsize\bfseries}
\titlespacing*{\section}{0mm}{2mm}{1mm}[0mm] % left top bottom right
\titleformat*{\subsection}{\normalsize\bfseries}
\titlespacing*{\subsection}{0mm}{2mm}{1mm}[0mm]
\titleformat*{\subsubsection}{\normalsize\bfseries\itshape}
\titlespacing*{\subsubsection}{0mm}{1mm}{0mm}[0mm]

\begin{document}
\pagestyle{CVfooter}

{\fontfamily{phv}\selectfont{

% \noindent\textbf{\uppercase{curriculum vitae}}
% \vspace{2mm}
\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
% \noindent\textbf{Patrick V.\ Phaneuf} & CV updates: \href{www.patrickphaneuf.com}{patrickphaneuf.com}  \\
\noindent\textbf{Patrick V.\ Phaneuf} & \href{https://github.com/pvphaneuf/cv/blob/main/PatrickPhaneufCV.pdf}{Curriculum Vitae}  \\
% \noindent\textbf{Patrick V.\ Phaneuf}\\
% \vspace{1mm}
% \noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
Ph.D. Candidate & Bioinformatics and Systems Biology  \\
University of California, San Diego & Email: \href{mailto:pphaneuf@eng.ucsd.edu}{pphaneuf@eng.ucsd.edu} \\
9500 Gilman Drive, Dept. 0419 & Phone: 458-207-1025\\
La Jolla, CA 92093-0419  & Canadian Citizen, US Legal Permanent Resident\\
\hline
\end{tabular*}

\section*{OBJECTIVE}
Genome engineering using both rational and data-driven methods.

\section*{EDUCATION AND TRAINING}
Ph.D. Bioinformatics and Systems Biology, \textit{expected} 2021, University of California, San Diego, CA \\
M.Sc. Computer Science, 2016, University of California, San Diego, CA \\
B.Sc. Computer Engineering, \textit{cum laude}, 2009, Mercer University, Macon, GA
% \begin{tabular}{l l l}
% Ph.D. Bioinformatics and Systems Biology &\textit{expected} 2021 &University of California, San Diego, CA \\
% M.Sc. Computer Science &2016 &University of California, San Diego, CA \\
% B.Sc. Computer Engineering, \textit{cum laude}, &2009 &Mercer University, Macon, GA \\
% \end{tabular}
\section*{SKILLS}
\begin{itemize}
\item\textbf{Bioinformatics}: Big Biological Data, Next Generation Sequencing, Alignment, Ensemble Pipelining, Read Trimming and Filtering, Mutation Calling, Assembly, Genome Annotation, Multiomics, Structural, and Network Biology.
\item\textbf{Data Science}: Statistics, Machine Learning, Graph Theory, Interactive Notebooks, Data Analytics and Visualization, Data Cleaning and Curation.
\item\textbf{Bioengineering and Biotechnology}: Adaptive Laboratory Evolution, Strain Design, Lab Automation, Flow Cytometry, Microfluidics
\item\textbf{Software Engineering}: Version Control, Test Driven Development, Continuous Integration and Deployment, Linting, Test Coverage, Static and Dynamic Analysis, Multithreaded, Multiprocess, TCP/IP.
\item\textbf{Programming}: C, C++, C\#, Python, R, Java, Javascript, SQL.
\item\textbf{High Performance Computing}: Cloud Compute and Storage, Containerization, Batch Processing.
\item\textbf{Web Development}: Full-Stack, Linux, Up Time Alerts, Web Analytics.
\item\textbf{Embedded}: Firmware, Oscilloscope Logic Analysis, In-Circuit Emulator Debugging, Soldering, Serial Communication, Robotics, Computer Vision
\item\textbf{Communication}: Scientific Publication, Standard Operating Procedures, Scientific and Business Presentations, Project Definition and Timeline, Team Organization and Task Assignment, English, French.
\item\textbf{Project Management}: Waterfall, Verification and Validation, Agile, Scrum, Quality Control and Assurance, Bug Tracking, Code Review, Requirements Analysis and Specifications, Feasibility and Merit Analysis, Root Cause Analysis, Milestone Roadmap, Product Lifecycle, Remote Workplace.
\end{itemize}

\section*{RESEARCH AND PROFESSIONAL EXPERIENCE}
\textbf{Systems Biology Research Group}, Ph.D. candidate advised by Dr. Adam Feist, 2014 -- present
\begin{itemize}
\item\textbf{Genome engineering using consolidated Adaptive Laboratory Evolution data} \\
Designed application-focused sequence changes to the \textit{E. coli} K-12 genome using a novel multi-dimensional adaptive laboratory evolution dataset, a graph-based genome annotation engine, and structural biology tools.
\item\textbf{Graph-based genome annotation engine and mutation enrichment} \\
Applied enrichment methods to mutations described by a novel multi-scale annotation framework and a consolidated set of experimental evolution conditions to automate key mutation identification and to deconvolute mutation selection pressures.
\item\textbf{Web-accessible experimental evolution mutation and conditions database} \\
Developed first version of a web-accessible database consolidating mutations from experiments executed by researchers across the field of experimental evolution. Managed further development and maintenance by a team of full-time software engineers.
\item\textbf{Ensemble mutation calling pipeline} \\
Developed initial versions of mutation calling pipeline used by scientific research institution and managed further development and maintenance by a team of full-time software engineers.
\end{itemize}
\vspace{1mm}
\textbf{Thermo Fisher Scientific}, Software and Firmware Engineer, 2010 -- 2014 \\
Developed system control software and firmware for the Attune® Acoustic Focusing Cytometer and Attune® Autosampler projects. Experience the complete product life-cycle for both a software and hardware product through a combination of the first and second iteration of the Attune®.

\section*{PUBLICATIONS}
\vspace{2mm}
\begin{bibunit}
\nocite{apsrev42Control}
\nocite{Phaneuf2020-ql-,Phaneuf2019-to,Rychel2020-vi,Lamoureux2020-so,Sandberg2020-gr,Heckmann2020-ia,Du2020-od,Anand2019-yy,Lloyd2019-sn,Anand2019-et,Guzman2018-wp,Pekar2018-dr,Yang2019-eb,Mundhada2017-rv}
\putbib[publications]
\end{bibunit}
}
\end{document}